\documentclass[11pt, a4paper, sans, color, final]{moderncv}
\usepackage[firstyear=1999, lastyear=2025]{moderntimeline}
\usepackage[scale=0.8, margin=0.8cm]{geometry}
\usepackage[utf8]{inputenc}

\moderncvstyle{classic}
\moderncvcolor{blue}
\tlenablemonths{}
\nopagenumbers{}

\colorlet{quotecolor}{color1}
\colorlet{sectioncolor}{color1}
\colorlet{bodyrulecolor}{color1}
\colorlet{firstnamecolor}{color1!50}

\name{Aurélien}{STÉBÉ}
\title{Freelance Tech Lead Software Engineer}
\address{France~-~Guadeloupe (UTC -4)\\\\}
\email{Aurelien.Stebe@gmail.com}
\social[github][github.com/AurelienStebe]{GitHub.com/AurelienStebe}
% \social[twitter][twitter.com/AurelienStebe]{Twitter.com/AurelienStebe}
\social[linkedin][linkedin.com/in/Aurelien-Stebe]{LinkedIn.com/AurelienStebe}

\newcommand{\website}[2][]{\textcolor{color1}{\link[#1]{#2}}}
\setlength{\hintscolumnwidth}{0.15\textwidth}

\tikzset{
  tl@startyear/.style={
    font=\scriptsize,
    name=tl@startyear,
    inner xsep=0pt,
    anchor=north,
  }
}

\tikzset{
  tl@endyear/.style={
    font=\scriptsize,
    name=tl@endyear,
    inner xsep=0pt,
    anchor=south,
  }
}

\begin{document}
\makecvhead

\centering
\begin{minipage}{0.888\textwidth}
  \quotestyle{
    Creative software developer with over 20 years of expertise in web technologies, from back to front.
    Adept at leading diverse remote teams and managing end-to-end projects delivering scalable solutions.
    Committed to smart collaborative technical leadership, meticulous quality, and relentless bug hunting.
    Passionate about cutting-edge technologies, modernizing legacy systems, and generative AI integrations.
  }
\end{minipage}\\[1.5em]

\section{Experience}
\tlcventry{2020/9}{0}{Freelance Tech Lead Engineer}{(via Toptal)}{}{\website{https://www.toptal.com/resume/aurelien-stebe}}{
  \begin{itemize}
    \item Managed full project lifecycles, from requirements analysis and feature planning to secure cloud deployments.
    \item Developed technical architectures for diverse web application projects using modern JavaScript frameworks.
    \item Engineered robust back-end systems with Python and Ruby, integrating advanced APIs and external services.
    \item Created and maintaining \website[``Gladdis'']{https://github.com/AurelienStebe/Gladdis}, an innovative open-source Obsidian plugin to support agentic AI natively.
  \end{itemize}
}

\vspace{0.8em}
\tlcventry{2017/6}{2020/8}{Senior Full Stack Principal Engineer}{Studio BeDesign (remote)}{}{\website{https://studio-bedesign.com}}{
  Established the complete IT infrastructure for a dynamic web agency by orchestrating the seamless
  migration from a legacy Django eCommerce platform to a custom WordPress solution. Developed a robust
  Docker-based deployment and hosting process while mentoring team members on modern web design and development.
}

\vspace{0.8em}
\tlcventry{2012/11}{2017/5}{Senior Full Stack Software Engineer}{Exelcia IT}{}{\website{https://www.exelcia-it.com}}{
  Joined an expert Java consultancy serving telecom and airline sectors, which more than tripled in 5 years.
  \vspace{0.4em}
  \begin{itemize}
    \item Participated in the challenging merger of two large customer support platforms (Orange Caraïbes \& Réunion).
    \item Specialized in Unix Server administration and Travel Data analysis tooling for multiple airline companies.
  \end{itemize}
}

\vspace{0.8em}
\tlcventry{2010/6}{2012/10}{Java Full Stack Software Engineer}{Telespazio (VEGA UK)}{}{\website{https://www.telespazio.com}}{
  Led the specification and implementation of an Operations Management Environment for ESA's Sentinel-1 mission.
  Developed a unified Grails-based web portal integrating ticketing (Jira), inventory (OCS), and document
  management (KnowledgeTree), collaborating closely with clients on taxonomy and workflow design.
}

\vspace{0.8em}
\tlcventry{2003/6}{2010/5}{Java Backend Software Engineer}{European Space Agency (ESA)}{}{\website{https://www.esa.int}}{
  Actively contributed to the \website[``International Virtual Observatory Alliance'' (IVOA)]{https://ivoa.net} efforts to
  create standards\\and implementations for the open and seamless publication, discovery, and analysis of astronomical data.
  \vspace{0.4em}
  \begin{itemize}
    \item Traveled with a team of 8 all over the world, giving talks in biannual conferences, leading workshops.
    \item Worked in autonomy on the Resource Registry Working Group, nominated Vice-Chairman for 3 years.
    \item Released the first fully Harvestable and Searchable Registry, adopted as the \website[official Euro-VO Registry]{http://registry.euro-vo.org}.
  \end{itemize}
}

\section{Education}
\tlcventry{1999/9}{2003/6}{Master of Computer Science}{ISEP~--~Institut Supérieur d'Électronique de Paris}{France}{}
{Graduate school of Software Engineering, Telecommunications, Networks \& Electronics, \website{https://en.isep.fr}}

\section{Tech Skills}
\cvdoubleitem{\textbf{Languages}}{JavaScript, TypeScript, Python, Ruby}{\textbf{Front-End}}{React, Vue, Svelte, TailwindCSS, Sass}
\cvdoubleitem{\textbf{Cloud Services}}{Docker, AWS, Azure, GCP, Firebase}{\textbf{JS Tooling}}{Rollup, Webpack, Vitest, Jest, Express}
\cvdoubleitem{\textbf{Databases}}{Relational, NoSQL, Elastic, GraphQL}{\textbf{Frameworks}}{Next/Nuxt.js, Vite, Django, WordPress}

\section{Soft Skills}
\cvdoubleitem{\textbf{Trilingual}}{Fluent in English, French and Spanish}{\textbf{Public Talk}}{Conferences, Presentations, Workshops}
\cvdoubleitem{\textbf{Architecture}}{Jamstack, Event-Driven, Microservices}{\textbf{Leadership}}{Cross-Functional Technical Knowledge}

\section{Interests}
\cvdoubleitem{\textbf{Hobbies}}{Gardening, sailing, aviation, apiculture}{\textbf{Sports}}{Brazilian Jiu-Jitsu, swimming, judo}

\clearpage
\end{document}
